Machine Learning Methods for Site-specific Input Management

### 2022-02-06 Codes/PrepareResults.rmd

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
    na.omit() %>%
    dplyr::rename(tgtn=NPlan,tgts=SRPlan)

data_dt <- data.table(data_sf) %>%
    setnames(names(.),tolower(names(.)))

tgts_ls <- data_dt[,tgts] %>% unique() %>% sort

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2],] %>%
  .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[,yield:= yield*62.77]

tree <- causalTree(
  yield ~ slope+ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
opfit <- prune(tree, opcp)

# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.png"))
fancyRpartPlot(opfit,sub='')
# dev.off()
```

>>>>

data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
  na.omit() %>%
  dplyr::rename(tgtn = NPlan, tgts = SRPlan)

data_dt <- data.table(data_sf) %>%
  setnames(names(.), tolower(names(.)))

tgts_ls <- data_dt[, tgts] %>%
  unique() %>%
  sort()

ctree_data <- copy(data_dt) %>%
  .[tgts %in% tgts_ls[1:2], ] %>%
  .[, treat := ifelse(tgts == tgts_ls[2], 1, 0)] %>%
  #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
  .[, yield := yield * 62.77]

tree <- causalTree(
  yield ~ slope + ecs,
  data = ctree_data,
  treatment = ctree_data$treat,
  split.Rule = "CT",
  cv.option = "CT",
  split.Honest = T,
  cv.Honest = T,
  split.Bucket = F,
  xval = 5,
  cp = 0,
  minsize = 20,
  propensity = 0.5
)

opcp <- tree$cptable[, 1][which.min(tree$cptable[, 4])]
opfit <- prune(tree, opcp)
```
